### 2023-07-11 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on stenosis example

@@

%\begin{comment}
%\begin{figure}[h]
\begin{figure*}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp6MCp5.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig5a.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig5b.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig5c.pdf}
  \caption{\label{fig:RA6} \small A vesicle passing through the stenosis
  geometry. The vesicle's reduced area is $\alpha = 0.6$ and the
  capillary number is $Ca = 0.25$. The vesicles are: (a)
  single-component with bending modulus $b=1$; (b) single-component with
  bending modulus $b=0.55$; (c) multicomponent.}
%\end{figure}
\end{figure*}
%\end{comment}

@@

To create more significant differences between the three cases, we
consider the same geometry, but for a vesicle with reduced area $\alpha
= 0.4$. Figure~\ref{fig:RA4} shows six time steps of a (a) stiff
single-component, (b) floppy single-component, and (c) multicomponent
vesicle. We first consider the three different energies---bending,
tension, and phase---for each of these cases.  In
Figure~\ref{fig:Energy}, we plot these energies as a function of the
vesicle's center. As a reminder, the vesicle enters the constriction at
$x=-15$ and exits at $x=15$. Also note that the single-component
vesicles do not have a phase energy. A few general trends can
immediately be seen. First, as the vesicle enters the stenosis, there
are sharp jumps in both the tension and bending energies, as expected.
Next, the multicomponent vesicles only coarsen when the vesicle is not
in the stenosis. Finally, when coarsening does occur, there are rapid
changes in the tension energy.

\begin{figure}
  \begin{minipage}{0.49\columnwidth}
    \centering
    \subfigimg[width=\textwidth]{(a)}{figures/Fig13a.pdf}
    \subfigimg[width=\textwidth]{(c)}{figures/Fig13c.pdf}
    \subfigimg[width=\textwidth]{(e)}{figures/Fig13e.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.49\columnwidth}
    \centering
    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
  \end{minipage}
  \caption{\label{fig:Energy} \small The Bending (blue), tension
  (yellow), and phase (red) energies for a (a/b) single-component
  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
  \todo[inline]{need to redo these plots}
\end{figure}

A main difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers in all six cases are
in Figure~\ref{fig:lubrication}. The tank-treading velocities of the
examples with reduced area $\alpha = 0.4$ are in
Figure~\ref{fig:tankTreadRAp4}. The vesicle shapes at the dashed black
lines are also included, and the four marker points are the Lagrangian
points where the tangential velocities are computed. For reduced area
$\alpha = 0.4$, the single-component ($b=1$) and multicomponent vesicles
are clearly tank treading. Since the single-component case has a larger
difference between its top and bottom boundary layers (see
Figure~\ref{fig:lubrication}), it tank treads faster than the
multicomponent case. In addition, since the top boundary layer is larger
in both cases, they both tank-tread in the same
direction---counterclockwise. In contrast, the single-component vesicle
with $b=0.55$ tank-treads in the clockwise direction; note, however,
that this example is still undergoing some deformations, so a constant
tank-treading velocity is not observed. When $\alpha = 0.6$, the vesicle
undergoes deformations while in the stenosis, and a constant
tank-treading velocity is not observed

@@

%\begin{figure}[h]
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(a)}{figures/Fig11c1.pdf}
%        \subfigimg[width=\textwidth]{(c)}{figures/Fig11b1.pdf}
%        \subfigimg[width=\textwidth]{(e)}{figures/Fig11a.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(a)}{figures/TankTreadRAp4Conc.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(c)}{figures/TankTreadRANoConcp55.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(e)}{figures/TankTreadRAp4NoConc.pdf}
%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6Conc.pdf}
%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6NoConc.pdf}
%    \end{minipage}
%    \hfill
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(b)}{figures/Fig11c2.pdf}
%        \subfigimg[width=\textwidth]{(d)}{figures/Fig11b2.pdf}
%        \subfigimg[width=\textwidth]{(f)}{figures/Fig11a2.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(b)}{figures/TankTreadRAp4ConcVes.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(d)}{figures/TankTreadRANoConcp55Ves.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(f)}{figures/TankTreadRAp4NoConcVes.pdf}
%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6ConcVes.pdf}
%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6NoConcVes.pdf}
%    \end{minipage}
%    \caption{\small The tangential velocity at four Lagrangian points on a (a) single-component vesicle with $b = 1$ (c) single-component vesicle with $b = 0.55$, and (e) multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all cases. (b/d/f) A corresponding vesicle shape with the Lagrangian points.
%    \label{fig:tankTreadRAp4}}
%\end{figure}
\begin{figure*}[t]
%\begin{figure}[htp]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/Layer_Size_RAp4_SC.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/Layer_Size_RAp4_SCp55.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
  \caption{\label{fig:tankTreadRAp4} \small The lubrication layer
  thicknesses (red and blue), excess pressure (green), and tank treading
  velocity of four Lagrangian points of a (a) stiff single-component
  vesicle, (b) floppy single-component vesicle, and (c) multicomponent
  vesicle. The reduced area is $\alpha = 0.4$ in all three cases. Also
  illustrated is the vesicle shape and the four Lagrangian points at the
  location indicated by the dash line. The black dashed line is the
  center line of the channel, and the arrow denotes the tank treading
  direction.}
%\end{figure}
\end{figure*}

@@

The size of the top and bottom lubrication layers are also related to
the excess pressure (Figure~\ref{fig:excessPressure}). If the
lubrication layers are large, most notably for the multicomponent
vesicle with reduced area $\alpha = 0.4$, then less pressure is required
to force the vesicle through the geometry, and we expect a smaller (less
negative) excess pressure. In contrast, if the lubrication layers are
small, most notably for the single-component vesicle with $b=1$ and
reduced area $\alpha = 0.4$, then more pressure is required to force the
vesicle through the geometry, and we expect a larger (more negative)
excess pressure.

@@

While the size of the lubrication layers affect the tank-treading
behavior and the excess pressure, it has almost no effect on the
migration speed of the vesicle. 
%In Figure~\ref{fig:vesVelocity}, we plot
%the average velocity of the vesicle as it passes through the stenosed
%region.
With the exception of the single-component vesicle with $b=1$ and
$\alpha = 0.6$, which has an average vesicle speed about 5\% slower, the
average vesicle speed is constant. Obviously, this average velocity
would be affected by the capillary number.

@@

When a vesicle is tank-treading near a solid wall, the flow in the thin
layer of fluid includes both a linear profile and a Poiseuille
profile~\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}.
The magnitude of the Poiseuille profile is determined by the pressure
gradient between the vesicle and the solid wall, while the linear
profile is determined by the tangential velocity of the vesicle relative
to the solid wall. Using the definition of the lubrication layer
outlined in Section~\ref{sec:LL}, we consider the flow profile inside
this lubrication layer in Figure~\ref{fig:BLvelocities}. We observe that
the Poiseuille coefficient can be either positive or negative, meaning
that the pressure in the lubrication layer switches signs. This behavior
is caused when the tangential force on the vesicle
\begin{align}
  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u},
\end{align}
where
\begin{align}
  \frac{\delta E^m}{\delta u} = \frac{a}{\epsilon} 
    (f'(u) - \epsilon^2 u_{ss}) + \frac{b'(u)}{2} \kappa^2
\end{align}
is the variational derivative of the membrane energy with respect to the
lipid concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
single-component case, the tangential force is $\mathbf{F}_\tt =
\sigma_s$ which is the usual Marangoni effect.

>>>>

%\begin{figure}[h]
\begin{figure*}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp6MCp5.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig5a.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig5b.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig5c.pdf}
  \caption{\label{fig:RA6} \small A vesicle passing through the stenosis
  geometry. The vesicle's reduced area is $\alpha = 0.6$ and the
  capillary number is $Ca = 0.25$. The vesicles are: (a)
  single-component with bending modulus $b=1$; (b) single-component with
  bending modulus $b=0.55$; (c) multicomponent.}
%\end{figure}
\end{figure*}

@@

@@

\begin{figure*}[h]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/SC_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/SCp55_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/MCp5_energy.pdf}
  \caption{\label{fig:Energy} \small The Bending (blue), tension (red),
  and phase (green) energies for a (a) stiff single-component, (b)
  floppy single-component, and (c) multicomponent vesicle. The reduced
  area is $\alpha = 0.4$. Note that the single-component vesicles do not
  have a phase energy.} 
\end{figure*}

To create more significant differences between the three cases, we
consider the same geometry, but for a vesicle with reduced area $\alpha
= 0.4$. Figure~\ref{fig:RA4} shows six time steps of a (a) stiff
single-component, (b) floppy single-component, and (c) multicomponent
vesicle. We first consider the three different energies---bending,
tension, and phase---for each of these cases. In
Figure~\ref{fig:Energy}, we plot these energies as a function of the
vesicle's center. As a reminder, the vesicle enters the constriction at
$x=-15$ and exits at $x=15$. Also note that the single-component
vesicles do not have a phase energy. A few general trends can
immediately be seen. First, as the vesicle enters the stenosis, it
develops regions of high curvature, and this results in an increase in
the bending energy. Also, since the stiff single-component vesicle
reaches a steady-state shape earlier, its tension and bending energies
remain nearly constant from $x=0$ until the end of the stenosis.
Regarding the multicomponent vesicle, the phase energy has sudden
decreases that correspond to the lipid phase coarsening. Note that this
coarsening only occurs when the vesicle is not in the stenosis. Finally,
when coarsening does occur, this results in a sudden change in the
bending and tension energies, but these energies almost instantly return
to their previous values once coarsening is complete.

%\begin{figure}
%  \begin{minipage}{0.49\columnwidth}
%    \centering
%    \subfigimg[width=\textwidth]{(a)}{figures/Fig13a.pdf}
%    \subfigimg[width=\textwidth]{(c)}{figures/Fig13c.pdf}
%    \subfigimg[width=\textwidth]{(e)}{figures/Fig13e.pdf}
%  \end{minipage}
%  \hfill
%  \begin{minipage}{0.49\columnwidth}
%    \centering
%    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
%    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
%    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
%  \end{minipage}
%  \caption{\label{fig:Energy} \small The Bending (blue), tension
%  (yellow), and phase (red) energies for a (a/b) single-component
%  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
%  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
%  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
%  \todo[inline]{need to redo these plots}
%\end{figure}

A main difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers for all three cases
of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
Figure~\ref{fig:lubricationComposite}. Also included in the bottom of
Figure~\ref{fig:lubricationComposite} are the tank-treading velocities.
The four marker points are the Lagrangian points where the tank-treading
velocities are computed, the black dashed line is the center line of the
channel, and the rounded arrow denotes the direction of rotation. The
stiff single-component and multicomponent vesicles are clearly tank
treading. Since the single-component case has a larger difference
between its top and bottom boundary layers, it tank treads faster than
the multicomponent case. In addition, since the top boundary layer is
larger in both cases, they both tank-tread in the same
direction---counterclockwise. In contrast, the floppy single-component
vesicle tank treads in the clockwise direction; note, however, that this
example is still undergoing some deformations, so a constant
tank-treading velocity is not observed.
%When $\alpha = 0.6$, the vesicle undergoes deformations while in the
%stenosis, and a constant tank-treading velocity is not observed

@@

%\begin{figure}[h]
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(a)}{figures/Fig11c1.pdf}
%        \subfigimg[width=\textwidth]{(c)}{figures/Fig11b1.pdf}
%        \subfigimg[width=\textwidth]{(e)}{figures/Fig11a.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(a)}{figures/TankTreadRAp4Conc.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(c)}{figures/TankTreadRANoConcp55.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(e)}{figures/TankTreadRAp4NoConc.pdf}
%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6Conc.pdf}
%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6NoConc.pdf}
%    \end{minipage}
%    \hfill
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(b)}{figures/Fig11c2.pdf}
%        \subfigimg[width=\textwidth]{(d)}{figures/Fig11b2.pdf}
%        \subfigimg[width=\textwidth]{(f)}{figures/Fig11a2.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(b)}{figures/TankTreadRAp4ConcVes.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(d)}{figures/TankTreadRANoConcp55Ves.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(f)}{figures/TankTreadRAp4NoConcVes.pdf}
%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6ConcVes.pdf}
%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6NoConcVes.pdf}
%    \end{minipage}
%    \caption{\small The tangential velocity at four Lagrangian points on a (a) single-component vesicle with $b = 1$ (c) single-component vesicle with $b = 0.55$, and (e) multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all cases. (b/d/f) A corresponding vesicle shape with the Lagrangian points.
%    \label{fig:tankTreadRAp4}}
%\end{figure}
\begin{figure*}[t]
%\begin{figure}[htp]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/Layer_Size_RAp4_SC.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/Layer_Size_RAp4_SCp55.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
  \caption{\label{fig:lubricationComposite} \small The lubrication layer
  thicknesses (red and blue), excess pressure (green), and tank treading
  velocity of four Lagrangian points of a (a) stiff single-component
  vesicle, (b) floppy single-component vesicle, and (c) multicomponent
  vesicle. The reduced area is $\alpha = 0.4$ in all three cases. Also
  illustrated is the vesicle shape and the four Lagrangian points at the
  location indicated by the dash line. The black dashed line is the
  center line of the channel, and the arrow denotes the tank treading
  direction.}
%\end{figure}
\end{figure*}

@@

The size of the top and bottom lubrication layers are also related to
the excess pressure. The green curve on the top half of
Figure~\ref{fig:lubricationComposite} shows the excess pressure with the
axis aligned on the right side of the plot. When the lubrication layers
are large, most notably for the multicomponent vesicle, less pressure is
required to force the vesicle through the geometry, and the result is a
smaller (less negative) excess pressure. In contrast, when the
lubrication layers are small, most notably for the stiff
single-component vesicle, more pressure is required to force the vesicle
through the geometry, and we the result is a larger (more negative)
excess pressure.

@@

%While the size of the lubrication layers affect the tank-treading
%behavior and the excess pressure, it has almost no effect on the
%migration speed of the vesicle. 
%%In Figure~\ref{fig:vesVelocity}, we plot
%%the average velocity of the vesicle as it passes through the stenosed
%%region.
%With the exception of the single-component vesicle with $b=1$ and
%$\alpha = 0.6$, which has an average vesicle speed about 5\% slower, the
%average vesicle speed is constant. Obviously, this average velocity
%would be affected by the capillary number.

@@

\todo[inline]{Bryan is here}
When a vesicle is tank-treading near a solid wall, the flow in the thin
layer of fluid includes both a linear profile and a Poiseuille
profile~\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}.
The magnitude of the Poiseuille profile is determined by the pressure
gradient between the vesicle and the solid wall, while the linear
profile is determined by the tangential velocity of the vesicle relative
to the solid wall. Using the definition of the lubrication layer
outlined in Section~\ref{sec:LL}, we consider the flow profile inside
this lubrication layer in Figure~\ref{fig:BLvelocities}. We observe that
the Poiseuille coefficient can be either positive or negative, meaning
that the pressure in the lubrication layer switches signs. This behavior
is caused when the tangential force on the vesicle
\begin{align}
  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u},
\end{align}
where
\begin{align}
  \frac{\delta E^m}{\delta u} = \frac{a}{\epsilon} 
    (f'(u) - \epsilon^2 u_{ss}) + \frac{b'(u)}{2} \kappa^2
\end{align}
is the variational derivative of the membrane energy with respect to the
lipid concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
single-component case, the tangential force is $\mathbf{F}_\tt =
\sigma_s$ which is the usual Marangoni effect.
